---
title: "Women's suffrage in America"
author: "Juan Ivan Cruz"
date: '2024-03-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Libraries**
Load the libraries that will be needed.
```{r,message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(maps)
library(plotly)
```
# **Data**
Women's suffrage data was extracted from Wikipedia (https://en.wikipedia.org/wiki/Timeline_of_women%27s_suffrage). Information is stored in dataset named "data" and then filtered to include only countrywide and full right events (since some countries approved women's suffrage with restrictions at the beginning.

```{r, message=FALSE, warning=FALSE}
data <- read_excel("D:/IWD.xlsx", sheet <- "Sheet1")
data<-filter(data, Level=="Countrywide", Type=="Full")

```

# **Map**
World map is displayed including a color scale indicating the year when full rights to vote in political elections where granted for women nationwide.
```{r}
plot_ly(data, type='choropleth',locations=data$Code,z=data$Year, text=data$Country, color=data$Year, colorscale="reds")%>%
  layout(geo=list(lonaxis=list(range=c(-180,0))))
```